Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-09-09 ms.tex
Line breaks added

\section{Introduction}
Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently favored hierarchical model of cosmic structure formation, larger objects formed through successive mergers of smaller
objects with galaxy clusters sitting a top this mass hierarchy \citep[see][for a review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark matter (DM), as indicated by galaxy dynamics and gravitational lensing \citep[][]{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the intra-cluster medium (ICM) contributes about 15\% of the total cluster mass and individual galaxies account for the remainder (about 5\%). The ICM gas mass also comprises a significant fraction of the observable (baryonic) matter in the Universe.

@@

Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons, in the form of protons and heavy ions, in the ICM is to be expected. The main energy-loss mechanism for CR hadrons at high energies is pion production through the interaction of CRs with nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and positrons,\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or positron as well as neutrinos.} and the neutral pion to gamma rays. Due to the low density of the ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996, article:Berezinsky_etal:1997} allowing them to accumulate over time.  Depending on the CR pressure, quantified by the CR-to-thermal pressure fraction $X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays can be expected.

@@

@@

The analysis of this work follows the same procedure as described in detail in \citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle cut of 105$^{\circ}$ is applied. The \emph{Fermi} Science Tools version v9r23p1 and Instrumental Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events calibrated  in flight) were used throughout this work. Only photons above 1 GeV are considered, where the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates the systematic uncertainties at 10 GeV to be around 20\%.\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.

@@

We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma, normalized to the total flux within the virial radius (dotted lines) and the angular apertures tested in this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval of 1--3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.  In our further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of 1--3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.

@@

Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest. In
the case of VERITAS, for the most constraining regions tested (within an aperture of radius
0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table
\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one at
energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure of
$X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius of
$X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining {\em Fermi}
upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger than our
model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral index for the
energy range of 1--3 GeV). Scaling our integrated relative CR pressure profile yields the
constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a limit within the cluster
virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}).

@@

\begin{enumerate}
\item Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we
  determine the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced
  synchrotron emission exactly matches the observed radio halo emission over the entire extent. To
  this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel integral
  equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio emissivity,
  \begin{equation}
    \label{eq:Coma:radio}
    j_{\nu} (r) = \frac{S_{0}}{2\pi\, r_{\rmn{c}}}\,
    \frac{6\beta - 1}{\left(1 + r^{2}/r_{\rmn{c}}^{2}\right)^{3 \beta}}\,
    \mathcal{B}\left(\frac{1}{2}, 3\beta\right)
    = j_{\nu,0} \left(1 + r^2/r_{\rmn{c}}^{2}\right)^{-3 \beta},
  \end{equation}
  where $\mathcal{B}$ denotes the beta function. It is generically true for weak magnetic fields
  ($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$
  (where $X_B$ denotes the magnetic-to-thermal energy density) has to increase by a factor of about
  100 toward the radio halo periphery to account for the observed extent. If we were to adopt a
  steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative
  CR pressure would have to rise accordingly by a factor of 100.

@@

The expected gamma-ray flux due to self-annihilations of WIMPs is given by 
\begin{equation}
\frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
\label{eqn:WIMPflux}
\end{equation}
where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends on the DM distribution.

Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. From Eq. (\ref{eqn:WIMPflux}) we get
\begin{equation}
\expval{\sigma v}(95\%\ \mathrm{CL}) > R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
\end{equation}
The astrophysical factor $J$ can be expressed as
\begin{equation}
J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right) \int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
\end{equation}
where $\lambda$ represents the line-of-sight. Because the self-annihilation of a WIMP is a two-body process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$. Here, $J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the Hubble radius, $R_{H}$.

@@

%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor no longer compensate for the increased count of background events and the signal-to-noise deteriorates.

@@

is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV, it falls below the flux upper limits which do not yet constrain the simulation model.

@@

\begin{deluxetable}{lccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
\tablehead{
                      & $1-3$ GeV & $3-10$ GeV & $10-30$ GeV\\
\small{Spatial Model} & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}} (\small{Significance})\\
\hline
\multicolumn{4}{c}{\small{Spectral index $\alpha=2.1$}}
}
\startdata
\small{Point Source} & 2.745 (0.302) & 0.965 (0.000) & 1.002 (1.313)\\
\small{Disk: r = 0.2$^\circ$} & 3.066 (0.648) & 1.193 (0.218) & 1.165 (2.031)\\
\small{Disk: r = 0.4$^\circ$} & 3.515 (0.768) & 1.297 (0.177) & 1.234 (2.349)\\
\cutinhead{\small{Spectral index $\alpha=2.3$}}
\small{Point Source} & 2.803 (0.317) & 0.992 (0.000) & 1.006 (1.371)\\
\small{Disk: r = 0.2$^\circ$} & 3.130 (0.654) & 1.227 (0.286) & 1.166 (2.072)\\
\small{Disk: r = 0.4$^\circ$} & 3.586 (0.787) & 1.341 (0.273) & 1.236 (2.380)\\
\cutinhead{\small{Spectral index $\alpha=2.5$}}
\small{Point Source} & 2.854 (0.333) & 1.016 (0.000) & 1.009 (1.424)\\
\small{Disk: r = 0.2$^\circ$} & 3.184 (0.658) & 1.259 (0.349) & 1.167 (2.112)\\
\small{Disk: r = 0.4$^\circ$} & 3.647 (0.804) & 1.381 (0.362) & 1.237 (2.408)\\
\enddata
\tablenotetext{a}{99\% confidence level upper limit in units of $10^{-10}$ ph. cm$^{-2}$ s$^{-1}$.}
\label{table:fermi}
\end{deluxetable}

\del{
\begin{deluxetable}{lcccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
\tablehead{
\colhead{Spatial model} & \multicolumn{3}{c}{S[$\sigma$]\tablenotemark{a}} & \multicolumn{3}{c}{Flux U.L.\tablenotemark{b}} \\
\colhead{} & \colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} & 
\colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} \\
\hline
\multicolumn{7}{c}{Spectral index $\alpha=2.1$ (fixed)}
}
\startdata
Point source & 0.30 & 0 & 1.3 & 1.73 & 4.87 & 0.627 \\
Disk, $r=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
Disk, $r=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
\cutinhead{Spectral index $\alpha=2.5$ (fixed)}
Point source & 0.33 & 0 & 1.42 & 1.81 & 0.526 & 0.635 \\
Disk, $r=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
Disk, $r=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
\enddata
\tablenotetext{a}{Statistical significance.}
\tablenotetext{b}{95\% confidence level upper limit in units of $10^{-10}$ ph. cm$^{-2}$ s$^{-1}$.}
\label{table:fermi}
\end{deluxetable}
}

@@

\begin{deluxetable}{ccc}
\tablecolumns{3}
\tablewidth{0pc}
\tablecaption{Astrophysical factors}
\tablehead{
\colhead{RoI [deg]} & $\expval{J}_{\rmn{signal}}$ [GeV$^{2}$ cm$^{-5}$ sr] & $\alpha\expval{J}_{\rmn{bkg}}$ [GeV$^{2}$ cm$^{-5}$ sr]
}
\startdata
0 & $5.7\times 10^{16}$ & $1.3\times 10^{14}$ (negligible) \\
0.2 & $8.1\times 10^{16}$ & $4.4\times 10^{14}$ ($<0.01\expval{J}_{\rmn{signal}}$, negligible) \\
0.4 & $9.4\times 10^{16}$ & $1.3\times 10^{15}$ ($\simeq0.01\expval{J}_{\rmn{signal}}$, negligible)
\enddata
\tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
\label{table:astrofactor}
\end{deluxetable}

>>>>

%
%

\section{Introduction}
Clusters of galaxies are the largest virialized objects in the Universe, with typical diameters of
a few Mpc and masses on the order of $10^{14}$ to $10^{15} M_{\odot}$. According to the currently
favored hierarchical model of cosmic structure formation, larger objects formed through successive
mergers of smaller objects with galaxy clusters sitting a top this mass hierarchy
\citep[see][for a review]{article:Voit:2005}. Most of the mass of a cluster is in form of dark
matter (DM), as indicated by galaxy dynamics and gravitational lensing
\citep{article:DiaferioSchindlerDolag:2008}. Baryonic gas making up the intra-cluster medium (ICM)
contributes about 15\% of the total cluster mass and individual galaxies account for the remainder
(about 5\%). The ICM gas mass also comprises a significant fraction of the observable (baryonic)
matter in the Universe.

@@

Galaxy clusters have for many years been proposed as sources of gamma rays. If shock acceleration
in the ICM is an efficient process, a population of highly relativistic cosmic-ray (CR) hadrons,
in the form of protons and heavy ions, in the ICM is to be expected. The main energy-loss
mechanism for CR hadrons at high energies is pion production through the interaction of CRs with
nuclei in the ICM. Pions are short lived and decay; the charged pions to electrons and positrons,
\footnote{A charged pion decays to a muon or antimuon, which subsequently decay to an electron or
positron as well as neutrinos.} and the neutral pion to gamma rays. Due to the low density of the
ICM ($n_{\mathrm{ICM}}\sim 10^{-3}$ cm$^{-3}$), the large scales of a cluster and the volume
filling magnetic fields in the ICM, CR hadrons will be confined in the cluster on timescales
comparable and longer than the Hubble time \citep[][]{article:Volk_etal:1996,
article:Berezinsky_etal:1997} allowing them to accumulate over time. Depending on the CR pressure,
quantified by the CR-to-thermal pressure fraction
$X_\CR=\expval{P_{\CR}}/\expval{P_{\mathrm{th}}}$, an observable flux of high-energy gamma rays
can be expected.

@@

%
%

@@

The analysis of this work follows the same procedure as described in detail in
\citet{article:Abdo_etal:2009}. To eliminate albedo gamma rays from the Earth limb, a zenith angle
cut of 105$^{\circ}$ is applied. The \emph{Fermi} Science Tools version v9r23p1 and Instrumental
Response Functions (IRFs) P6\_V11\_Diffuse (a model of the spatial distribution of photon events
calibrated  in flight) were used throughout this work. Only photons above 1 GeV are considered,
where the constraints on the flux are most meaningful. The \emph{Fermi}-LAT collaboration estimates
the systematic uncertainties at 10 GeV to be around 20\%.
\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/LAT\_caveats.html}} Flux upper limits
at the 99\% confidence level in the energy range 1--30 GeV, assuming both a unresolved, point-like
or spatially extended emission, are tabulated in Table \ref{table:fermi}. The gamma-ray emission is
assumed to follow a power-law distribution with a photon index $\alpha=2.1$, 2.3, and $2.5$.

%
%

@@

We adopt the electron density profile for the Coma cluster that has been inferred from ROSAT X-ray
observations \citep{article:BrielHenryBohringer:1992} and model the spatial and spectral
distribution of CRs according to the model by \citet{article:PinzkePfrommer:2010} that neglects the
contribution of cluster galaxies. Figure \ref{fig:spectrum} shows the expected spectrum of Coma,
normalized to the total flux within the virial radius (dotted lines) and the angular apertures
tested in this study (solid lines). The gamma-ray flux limit of {\em Fermi} in the energy interval
of 1--3 GeV ($<0.4^\circ$) is most constraining. However, since the model flux within the finite
energy range of 1--3 GeV is smaller by a factor of 1.5 in comparison to the total flux above 1 GeV,
it falls below the flux upper limits which do not yet constrain the simulation model. In our
further analysis, we use the most constraining {\em Fermi} flux limits in the energy interval of
1-3 GeV as well as the gamma-ray flux limits of VERITAS in the energy range above 220 GeV.

@@

Table \ref{table:constraints} shows the expected gamma-ray fluxes within the regions of interest.
In the case of VERITAS, for the most constraining regions tested (within an aperture of radius
0.2$^{\circ}$), those are a factor of 7.2 below the inferred upper limits of VERITAS (see Table
\ref{table:results} and assuming a spectral index of $\alpha=2.3$ which matches the simulated one
at energies $E_\gamma=200$ GeV). Hence we scale the averaged relative CR pressure of our model by
that factor, keep the spatial behavior and obtain an integrated limit of the relative CR pressure
of $X_{\CR}<0.105$ within 0.2$^{\circ}$ that translates to a limit within the cluster virial radius
of $X_\CR<0.152$ (solid lines of Figure \ref{fig:xcr}). Equivalently, the most constraining
{\em Fermi} upper limit in the energy interval of 1--3 GeV ($<0.4^\circ$) is a factor of 1.1 larger
than our model predictions (assuming $\alpha=2.1$ which is very close to the simulated spectral
index for the energy range of 1-3 GeV). Scaling our integrated relative CR pressure profile yields
the constraint of $X_{\CR}<0.018$ within 0.4$^{\circ}$ that translates to a limit within the
cluster virial radius of $X_\CR<0.024$ (dashed lines of Figure \ref{fig:xcr}).

%
%

@@

\begin{enumerate}
\item
Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
the profile of the relative CR pressure, $X_{\CR}(r)$, so that the hadronically produced
synchrotron emission exactly matches the observed radio halo emission over the entire extent. To 
this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel
integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio
emissivity,

\begin{equation}
\label{eq:Coma:radio}
j_{\nu} (r) = \frac{S_{0}}{2\pi\, r_{\rmn{c}}}\,
\frac{6\beta - 1}{\left(1 + r^{2}/r_{\rmn{c}}^{2}\right)^{3 \beta}}\,
\mathcal{B}\left(\frac{1}{2}, 3\beta\right)
= j_{\nu,0} \left(1 + r^2/r_{\rmn{c}}^{2}\right)^{-3 \beta},
\end{equation}
where $\mathcal{B}$ denotes the beta function. It is generically true for weak magnetic fields
($B<B_{\rmn{CMB}}$) in the outer parts of the Coma halo that the product $X_{\CR}(r)X_{B}(r)$
(where $X_B$ denotes the magnetic-to-thermal energy density) has to increase by a factor of about
100 toward the radio halo periphery to account for the observed extent. If we were to adopt a
steeper magnetic decline such as $\alpha_{B}=0.5$ which produces a flat $X_{B}(r)$, the relative CR
pressure would have to rise accordingly by a factor of 100.

@@

The expected gamma-ray flux due to self-annihilations of WIMPs is given by 
\begin{equation}
\frac{d\Phi_{\gamma}(\Delta\Omega,E)}{dE}=
\frac{\expval{\sigma v}}{8\pi m_{\chi}^{2}}\frac{dN(E,m_{\chi})}{dE} J(\Delta\Omega),
\label{eqn:WIMPflux}
\end{equation}
where $\expval{\sigma v}$ is the thermally averaged product of the total self-annihilation cross
section and the WIMP velocity, $m_{\chi}$ is the WIMP mass, $dN(E,m_{\chi})/dE$ is the differential
gamma-ray yield per annihilation, $\Delta\Omega$ is the observed solid angle, and $J$ is the
astrophysical factor - a dimensionless factor which determines the DM annihilation rate and depends
on the DM distribution.

Given the upper limit on the observed gamma-ray rate, $R_{\gamma}(95\%\ \mathrm{CL})$, we can place
constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. From Eq.
(\ref{eqn:WIMPflux}) we get
\begin{equation}
\expval{\sigma v}(95\%\ \mathrm{CL}) > 
R_{\gamma}(95\%\ \mathrm{CL}) \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}
\frac{1}{\int^{m_{\chi}} dE A_{\mathrm{eff}}dN_{\gamma}/dE}
\end{equation}
The astrophysical factor $J$ can be expressed as
\begin{equation}
J(\Delta\Omega)=\left(\frac{1}{\rho_{c}^{2}R_{H}}\right)
\int_{\Delta\Omega}d\Omega\int d\lambda \rho^{2}(\lambda,\Omega),
\end{equation}
where $\lambda$ represents the line-of-sight. Because the self-annihilation of a WIMP is a two-body
process, $J(\Delta\Omega)$ is proportional to the square of the DM density $\rho$. Here,
$J(\Delta\Omega)$ has been normalized to the square of the critical density, $\rho_{c}$, and the
Hubble radius, $R_{H}$.

@@

%When the size of the integration region is increased, the limits on $\expval{\sigma v}$ result
%from a competition between the gain in the astrophysical factor $\expval{J}$ and the integrated
%background. For integration regions larger than 0.2$^{\circ}$ in radius, the astrophysical factor
%no longer compensate for the increased count of background events and the signal-to-noise
%deteriorates.

%
%

@@

@@

\begin{deluxetable}{lccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
\tablehead{
                      & $1-3$ GeV & $3-10$ GeV & $10-30$ GeV\\
\small{Spatial Model} & \small{Flux U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux
U.L.\tablenotemark{a}} (\small{Significance}) & \small{Flux U.L.\tablenotemark{a}}
(\small{Significance})\\
\hline
\multicolumn{4}{c}{\small{Spectral index $\alpha=2.1$}}
}
\startdata
\small{Point Source} & 2.745 (0.302) & 0.965 (0.000) & 1.002 (1.313)\\
\small{Disk: r = 0.2$^\circ$} & 3.066 (0.648) & 1.193 (0.218) & 1.165 (2.031)\\
\small{Disk: r = 0.4$^\circ$} & 3.515 (0.768) & 1.297 (0.177) & 1.234 (2.349)\\
\cutinhead{\small{Spectral index $\alpha=2.3$}}
\small{Point Source} & 2.803 (0.317) & 0.992 (0.000) & 1.006 (1.371)\\
\small{Disk: r = 0.2$^\circ$} & 3.130 (0.654) & 1.227 (0.286) & 1.166 (2.072)\\
\small{Disk: r = 0.4$^\circ$} & 3.586 (0.787) & 1.341 (0.273) & 1.236 (2.380)\\
\cutinhead{\small{Spectral index $\alpha=2.5$}}
\small{Point Source} & 2.854 (0.333) & 1.016 (0.000) & 1.009 (1.424)\\
\small{Disk: r = 0.2$^\circ$} & 3.184 (0.658) & 1.259 (0.349) & 1.167 (2.112)\\
\small{Disk: r = 0.4$^\circ$} & 3.647 (0.804) & 1.381 (0.362) & 1.237 (2.408)\\
\enddata
\tablenotetext{a}{99\% confidence level upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
\label{table:fermi}
\end{deluxetable}

\del{
\begin{deluxetable}{lcccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core}
\tablehead{
\colhead{Spatial model} & 
\multicolumn{3}{c}{S[$\sigma$]\tablenotemark{a}} & 
\multicolumn{3}{c}{Flux U.L.\tablenotemark{b}} \\
\colhead{} & 
\colhead{1-3 GeV} & 
\colhead{3-10 GeV} & 
\colhead{10-30 GeV} & 
\colhead{1-3 GeV} & 
\colhead{3-10 GeV} & 
\colhead{10-30 GeV} \\
\hline
\multicolumn{7}{c}{Spectral index $\alpha=2.1$ (fixed)}
}
\startdata
Point source & 0.30 & 0 & 1.3 & 1.73 & 4.87 & 0.627 \\
Disk, $r=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
Disk, $r=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
\cutinhead{Spectral index $\alpha=2.5$ (fixed)}
Point source & 0.33 & 0 & 1.42 & 1.81 & 0.526 & 0.635 \\
Disk, $r=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
Disk, $r=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
\enddata
\tablenotetext{a}{Statistical significance.}
\tablenotetext{b}{95\% confidence level upper limit in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$.}
\label{table:fermi}
\end{deluxetable}
}

@@

\begin{deluxetable}{ccc}
\tablecolumns{3}
\tablewidth{0pc}
\tablecaption{Astrophysical factors}
\tablehead{
\colhead{RoI [deg]} &
\colhead{$\expval{J}_{\rmn{signal}}$ [GeV$^{2}$ cm$^{-5}$ sr]} & 
\colhead{$\alpha\expval{J}_{\rmn{bkg}}$ [GeV$^{2}$ cm$^{-5}$ sr]}
}
\startdata
0 & $5.7\times 10^{16}$ & $1.3\times 10^{14}$ (negligible) \\
0.2 & $8.1\times 10^{16}$ & $4.4\times 10^{14}$ ($<0.01\expval{J}_{\rmn{signal}}$, negligible) \\
0.4 & $9.4\times 10^{16}$ & $1.3\times 10^{15}$ ($\simeq0.01\expval{J}_{\rmn{signal}}$, negligible)
\enddata
\tablecomments{$\expval{J}_{\rmn{bkg}}$ is the astrophysical factor calculated for the background
region (ring method) and is used to estimate the level of gamma-ray contamination from DM.}
\label{table:astrofactor}
\end{deluxetable}
